In this manuscript 
 
Inspired by previous projects (\citep{Amarante2019, Wijnen2014}), we present a fully integrated, and characterized, system for micro-litter range fluid delivery targeted towards neuroscience behaviour experiments. 
 
We designed a simple protocol which allowed us provide an extensive characterization of trial-to-trial variability in the fluid delivery dynamics. An import stack of tests when considering the intended use of this system for rodent behaviour experiments.
We provide an alternative to gravity-based passive systems, by providing a scalable and affordable solution that allows for dynamic control over reward delivery, without suffering from the long-term stability problems often associated with the former systems. Additionally, we also highlight the afforded control gained over flow-rate that such an non-passive system allows.
Importantly, we also tested the compatibility of the system with common neuroscience experimental demands by deploying it during rodent behaviour and electrophysiological experiments.

Finally, we provide users with an interface to control the system by leveraging the Harp protocol. Adopting this standard, affords the integration of hereto system into a broader, and more mature, experimental ecosystem powered by Bonsai. For example, given the capabilities that this software already offers to interact with other hardware (\textit{e.g.} cameras, electrophysiology, Arduino, audio, rendering of visual stimuli, among others.), we hope that such integration might lead to synergistic benefits to this ecosystem. 