 \leadauthor{Cruz}

\title{A flexible fluid delivery system for rodent behavior experiments}
\shorttitle{}

\author[1,2,3]{Bruno F. Cruz}
\author[1]{Paulo Carriço}
\author[1]{Luís Teixeira}
\author[1]{Sofia Freitas}
\author[1]{Filipe Mendes}
\author[1]{Dario Bento}
\author[1,\Letter]{Artur Silva}
\affil[1]{Champalimaud Research, Champalimaud Foundation, Lisbon, Portugal}
\affil[2]{NeuroGEARS Ltd, London, United Kingdom}
\affil[3]{Current address: Allen Institute for Neural Dynamics, Seattle, United States}
\date{}

\maketitle

\begin{abstract}
\input{Chapters/Abstract.tex}

\end{abstract}


\begin{corrauthor}
artur.silva\at research.fchampalimaud.org
\end{corrauthor}

\section*{Introduction}\label{s:introduction}
\input{Chapters/Introduction.tex}

\section*{Results}\label{s:results}
\input{Chapters/Results.tex}

\section*{Discussion}\label{s:discussion}
\input{Chapters/Discussion.tex}

\section*{Methods}\label{s:methods}
\input{Chapters/MaterialsAndMethods.tex}

\subsection*{Code and data availability}\label{s:code_availability}
All code and data related to the device characterization shown in this manuscript are available from \url{https://github.com/fchampalimaud/syringe.pump.manuscript}.

\subsection*{Acknowledgments}\label{s:acknowledgments}
We thank Cindy Poo, Hugo Marques and Tiago Monteiro for comments on the manuscript, and Gonçalo Lopes for help with the Bonsai interface.

\subsection*{Author's Contribution}\label{s:contributions}
B.C. and A.S. collected and analyzed data for the device characterization. P.C. and F.M designed and build the mechanical device. A.S. designed the PCB. D.B. assembled the PCB and initial data collection. L.T. wrote the firmware and graphical user interface, with input from A.S.. S.F. and B.C. designed the animal experiments. S.F. collected and analyzed data from rat behavior experiments. B.C. collected and analyzed data from the acute electrophysical experiments. B.C. made the figures in the manuscript. B.C. and A.S. wrote the manuscript with input from S.F. and L.T.


\section*{Bibliography}

\bibliography{refslist}

